---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dpi = 192,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jbplot

<!-- badges: start -->
[![R-CMD-check](https://github.com/jabenninghoff/jbplot/workflows/R-CMD-check/badge.svg)](https://github.com/jabenninghoff/jbplot/actions)
[![lint](https://github.com/jabenninghoff/jbplot/workflows/lint/badge.svg)](https://github.com/jabenninghoff/jbplot/actions)
<!-- badges: end -->

## Overview

**`r packageDescription("jbplot", fields = "Title")`:** `r packageDescription("jbplot", fields = "Description")`

Feel free to use and/or fork this project!

## Installation

You can install the development version of jbplot from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jabenninghoff/jbplot")
```
Or using renv:

``` r
# install.packages("renv")
renv::install("jabenninghoff/jbplot")
```

## Development

- Changelog: See "Changelog" or `NEWS.md`.
- Planned: [TODO](TODO.md)

## Examples

jbplot allows creation of styled plots, such as this `mtcars` example, adapted from `ggplot2::theme_minimal()`:

```{r mtcars, message = FALSE, warning = FALSE}
library(ggplot2)
library(jbplot)

ggplot(mtcars, aes(x = wt, y = mpg, color = factor(cyl))) +
  geom_point() +
  labs(
    title = "Fuel economy declines as weight increases",
    subtitle = "(1973-74)",
    caption = "Data from the 1974 Motor Trend US magazine.",
    x = "Weight (1000 lbs)",
    y = "Fuel economy (mpg)",
    color = "Gears"
  ) +
  theme_quo() +
  scale_color_viridis_d()
```

For more information, see the "jbplot ggplot2 style" [vignette](https://jabenninghoff.github.io/jbplot/articles/jbplot-style.html).
