---
title: "jbplot ggplot2 style"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{jbplot ggplot2 style}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE, warning = FALSE}
library(jbplot)
library(ggplot2)
library(showtext)

font_add_google("Lato", "Lato")
```

`jbplot` includes functions to change the style of [ggplot2](https://ggplot2.tidyverse.org) plots.
The included theme, quo, can be added to individual plots using `theme_quo()`.

## Quo Theme

The quo theme applied to the venerable `mtcars` dataset. Example adapted from
`ggplot2::theme_minimal()`:

```{r p1, fig.showtext = TRUE}
p1 <- ggplot(mtcars, aes(x = wt, y = mpg, color = factor(cyl))) +
  geom_point() +
  labs(
    title = "Fuel economy declines as weight increases",
    subtitle = "(1973-74)",
    caption = "Data from the 1974 Motor Trend US magazine.",
    tag = "Figure 1",
    x = "Weight (1000 lbs)",
    y = "Fuel economy (mpg)",
    color = "Gears"
  )

p1
p1 + theme_quo()
```

The viridis color scheme can be added manually using `ggplot2::scale_color_viridis_d()`:

```{r p1_viridis, fig.showtext = TRUE}
p1 +
  theme_quo() +
  scale_color_viridis_d()
```

## Viridis Quo

Quo is designed to be paired with the viridis color scale, added by calling one of the continuous
(c) or discrete (d) viridis color scales:

- `ggplot2::scale_color_viridis_c()`
- `ggplot2::scale_fill_viridis_c()`
- `ggplot2::scale_color_viridis_d()`
- `ggplot2::scale_fill_viridis_d()`

Sample plots using the default theme and color scales:

```{r txsamp}
txsamp <- subset(txhousing, city %in% c("Houston", "Fort Worth", "San Antonio", "Dallas", "Austin"))

(d <- ggplot(data = txsamp, aes(x = sales, y = median)) +
  geom_point(aes(colour = city)))
(p <- ggplot(txsamp, aes(x = median, fill = city)) +
  geom_histogram(position = "dodge", binwidth = 15000))
(v <- ggplot(faithfuld) +
  geom_tile(aes(waiting, eruptions, fill = density)))
```

The same plots after applying viridis and quo:

```{r viridis_quo, fig.showtext = TRUE}
d + scale_color_viridis_d() + theme_quo()
p + scale_fill_viridis_d() + theme_quo()
v + scale_fill_viridis_c() + theme_quo()
```

## Grid lines

Grid lines can be selectively disabled using `theme_quo()`:

```{r panel.grid, fig.showtext = TRUE}
d + scale_color_viridis_d() + theme_quo(minor = FALSE)
p + scale_fill_viridis_d() + theme_quo(x = FALSE)
v + scale_fill_viridis_c() + theme_quo(major = FALSE, minor = FALSE)
```
